Supramolecular crocodile line controls the rheological properties of polyelectrolytes hydrogels

### 2016-01-06 PALSE/ion_pairing_paper.tex
rewrite abstract and title with "crocodile line"

\title{Controlling the rheological properties of well-defined polyelectrolytes hydrogels by fine tuning their ion pairing process}

@@

\begin{abstract}
Starting from a common polymeric platform with lateral bromine substitution and phosphonate end group, it is possible, through two subsequent synthetic steps to generate a variety of poly(ionic liquids) with various cation/anion pair combinations. Upon water addition, the behavior of the resulting hydrogels is seen to be strongly dependent on the polymer structure, illustrating the possibility to control the gel formation properties by fine tuning of the intra and intermolecular ion pairing process.
\end{abstract}

>>>>

\title{Supramolecular crocodile line controls the rheological properties of polyelectrolytes hydrogels}
%\title{Controlling the rheological properties of well-defined polyelectrolytes hydrogels by fine tuning their ion pairing process}

@@

\begin{abstract}
We demonstrated recently that polyelectrolytes with cationic moieties along the chain and a single anionic head are able to form physical hydrogels due to the reversible nature of the head-to-body ionic bond. Here we generate a variety of such polyelectrolytes with various cationic moieties and counter-ions combinations starting from a common polymeric platform. We show that the rheological properties (shear modulus, critical strain) of the final hydrogels vary by three orders of magnitude depending on the cation/pair. Our data are well described by a theoretical model involving a supramolecular crocodile line between cross-links, the length of the line being set by the amount of charge dissociation.
\end{abstract}
